\chapter{Scenario 1}

\paragraph{Theme} Action/Adventure.
\paragraph{Goal} Survive environment. Find food/water, resist the elements, and find off attacks from the tribals.
\paragraph{Plot} Geographic Progression. The players are travelling from A to B. 
\paragraph{Climax} There is no end. 
\paragraph{Moral Quandry 1} Cannibalism.
\paragraph{Moral Quandry 2} Slugs.
\paragraph{Moral Quandry 3}  


\paragraph{Mirage} This desert phenomenon occurs only during the day. Usually it will be seen some distance away, and will disappear upon being approached within 100 yards. The length of time in the desert and the physical state of the party determines how easy it is to recognize a mirage. Roll 1d6 to determine the type of mirage:
\begin{enumerate}
    \item Caravan. Many camels are seen at a distance of 2 miles. They are travelling in a random direction.
    \item Sandstorm. 
    \item Oasis. Appearing as a large body of water.
    \item Heat haze. Caused by natural gass emissions. 
\end{enumerate}

\paragraph{Meteor Shower} The night sky is suddenly alive with streaming lights. Like giant fireflies, they streak from a position directly overhead towards the eastern horizon. They act almost as an arrow to point where you should go... or perhaps should not go. 

\paragraph{Shooting star} The night sky is lightened to incredible brilliance by a giant fire that appears from the east. The fire grows larger and larger as it streaks towards to (insert direction desired) horizon. The night sky is inky black after its passage.

\paragraph{Night Frost} This event can only occur after the desert sands cool sufficiently, usually late at night. The chill of the desert night strikes into the bones. The entire desert area becomes brilliant as crystal. In the morning after the frost has passed, the desert will be alive with tiny flowers, painting the land in beautiful hues. Within a hour of daylight, the flowers have withered in the sun to leave the desert as barren as it ever was.

\subsection{Animal Encounters}

\paragraph{An Old Stubborn Camel} If loaded with cargo it refuses to move, and even spit in the eyes of an aggressor if they persist, likely blinding them. The camel is an old and experienced desert traveller and knows the shortest route to the closest water source. If left alone, it will take that route to it.