\pagecolor{gray}\afterpage{\nopagecolor}
\fontfamily{pzc}
\selectfont
Co-Consul of Ablon enters the Office and the General Autorius sits at his table, golden goblets of wine and a plate full of grapes rests easy in front of him. 

``We had an agreement, that we'd share all revenue.''

``Yes''

``Hereopolis has agreed to give you 20,000 pounds of gold. I want my share.''

``Who told you this?''

``You deny?''

``Who told him.''

``I have spies among his people.''

``If Herod is kind enough to give me a gift, what business is it of yours? A gift is not revenue.''

It is not a gift, it is a bribe. For political and military favours. The cost of which favours shall be born by the state.''

``Peasantry.''

``Let us be realistic. This arrangement of ours can not work if you seek every opportunity to aggrandize yourself at my expense.''

``Laughter. Aggrandize myself. This from the boy whose so called father has been declared a God.''

``An honour he well deserves.''

``You only did it so you might be known as the Son of a God. You have no accomplishments of your own, so you seek to borrow the glory of others.''

``Its true, it was no accomplishment to defeat you at Mutina.''

``You defeated me? You cowardly little shit. You never left your tent. You have never defeated me, in anything.''

``Gentlemen, lets not get overheated. Im sure we can come to some reasonable agreement. I had hoped that you had learnt some humility and discipline. You are still the same old crude, arrogant, lech that you always were.''

``Thats right. Just the same. The same that is still fucking your mother!''
\normalfont