
\paragraph{Situational}
\begin{tabular}{l l}
Situational Combat & Modifier \\
\hline

\end{tabular}

\paragraph{Cover rules} \begin{tabular}{l l l }
Cover Type & AC Adj & Examples\\
\hline
1/4 Cover & +2 AC & \\
1/2 Cover & +4 AC & \\
3/4 Cover & +6 AC & \\
Full Cover & +10 AC & \\
\end{tabular}

\paragraph{Critical Hit Table}

\begin{tabular}{l l}
1 & Knock opponent down \\
2 & Head blow, teeth shatter, 1d4 damage, can't eat until healed\\
3 & Ear cut off, 1 point of damage\\
4 & Chop off 1-4 fingers, 1 point of damage per finger \\
5 & Crushing/Stabbing blow, blade stuck in rib cage. Reduces AC by 2, 1d8 damage per round \\
6 & Crush bone, render one limb of opponent useless, 1d8 damage\\
7 & Jaw destroyed, 1d8 damage, can’t speak or eat \\
8 & Elbow shattered by blow, arm crippled, 1d8 damage\\
9 & Knee shattered by blow, crippled can’t walk, 1d10 damage \\
10 & Crushing blow to opponent’s chest, collapsed lung, 1d10 damage, constitution cut in half \\
11 & Gut wound, spleen ruptures or is punctured, 1d12 damage\\
12 & Slice opponents in the face, blinded in both eyes \\
13 & Lung punctured; reduce constitution by 50\% per round until 0, then death \\
14 & Head blow, force knocks eye out of socket, explodes globe, blind in that eye, 1d10 damage \\
15 & Massive blow to chest, victim’s chest collapses, can’t breath, death in 1d4 rounds unless healed \\
16 & Sever artery, if wound goes untreated 1d12 damage per round until healed \\
17 & Chop off random limb, 1d12 points of bleed damage until wound staunched \\
18 & Crushing blow to the skull, opponent knocked unconscious, 1d12 points damage \\
19 & Eviscerated, instant death \\
20 & Chop off opponent’s head, instant death \\

\end{tabular}

\begin{multicols}{2}



\paragraph{Morale} 

\begin{itemize}
    \item Opponents start a fight when the group does not wish to fight.    \item Opponents display vastly superior magic or fighting ability.    \item Half the group is slain or incapaci- tated.    \item Members of the group have already fled.    \item The group’s leader is slain or incapacitated.    \item Opponents kill a significant number of the group in a single round.    \item Opponents display willingness to escalate the fight (killing in a fight that was previously non-lethal).    \item Reinforcements arrive to shore up the opponents’ numbers.    \item An individual is badly wounded (less than half hit points).    \item Opponents make an offer to accept a surrender.
\end{itemize}

\paragraph{Situational}

\begin{itemize}
    \item Fighting with no escape route.
    \item Fighting to defend one’s home or lair.    \item Fighting to defend loved ones or innocents.    \item The expectation that the enemy will slay incapacitated prisoners if victorious.    \item The expectation that the enemy will torture prisoners if victorious.    \item The expectation that the enemy will be merciful if victorious.    \item The knowledge that if the combatant is incapacitated but their side wins the fight they will be healed.    \item The fear of being executed (or worse) for cowardice if they run.    \item A creature is fighting for reasons of desperation (e.g. extreme hunger or maddening pain).    \item A previous offer to surrender has not been accepted.
\end{itemize}
\end{multicols}

