\chapter{Example Sheets}

These kinds of characters are by and large pulp fantasy, or what some call sword and sorcery style. The characters are morally ambigious but not outright villainous. They are not what you would call heroes. To put it another way, they are very Human, full of foibles and flaws that lend a rough verisimilitude to the adventures. They are, at least in part, motivated by wealth and power - but you have plenty of room to shape how that fits. There are no "dark lord" types except insofar as such antagonists stand in the way of a pulp fantasy character's achieving wealth, power, or the company of a beautiful woman. Feel free to modify any of the example characters as it suits your needs for your campaign. 

\begin{framed}\centeringIn this system we aim for character sheets to be fast to build, easy and elegant and not cloggy to record. You will find that the vast majority of your writings will be recording XP and the inventory. 
\end{framed}


    \section{Human Fighters}
        \subsection{The Hulking Brute} STR 18 (+3) DEX 14 (+1) CON 15 (+1) INT 6 (-1) WIS 9 (+0) CHA 11 (+0). Fighter. HP 11. Primary Attributes: STR, DEX, CON. Archetype: Greatsword Wielder. Carrying Capacity: 26
        
        Inventory: Greatsword. Scalemail.
        

        \subsection{The Cunning Mercenary} STR 12 (+0) DEX 13 (+1) CON 10 (+0) INT 16 (+2) WIS 9 (+0) CHA 11 (+0). Fighter. HP 10. Primary Attributes: STR, DEX, INT. Archetype: Sword and Board. Carrying Capacity: 16. 
        
        Inventory: Longsword. Studded leather. Parrying Dagger. 
        
        \subsection{The Dashing Swordsman} STR 12 (+0) DEX 13 (+1) CON 14 (+1) INT 10 (+0) WIS 11 (+0) CHA 16 (+2). Fighter. HP 11. Primary Attributes: STR, DEX, CHA. Archetype: Swordsman. Carrying Capacity: 16. 
        
        Inventory: Longsword. Fine mail. Heavy Steel Shield. 
        \subsection{Dead Man Walking} STR 15 (+1) DEX 8 (+0) CON 5 (-2) INT 10 (+0) WIS 13 (+1) CHA 13 (+1). Fighter. HP 8. Primary Attributes: STR, WIS, INT. Archetype: Pikeman. Carrying Capacity: 19. 
        
        Inventory: Pike. Shortsword. Small Steel Shield. Studded Leather Armour.
        
        Background: This man feels that, for whatever reason, his life is a ticking time bomb and that his life is a flickering light that can extinguish at any time. For some reasons his health is degraded, perhaps he survived a terrible afflication but has left his body wrecked. Now, with time running out, he has decided to dedicate his life to something worth remembering. 
        
        \subsection{The Hanged Man} STR 15 (+1) DEX 14 (+1) CON 18 (+3) INT 9 (+0) WIS 6 (-1) CHA 11 (+0). Fighter. HP 13. Primary Attributes: STR, DEX, CON. Archetype: Cutt throat. Carrying Capacity: 23. 
        
        Inventory: Shortsword. Mercy Giver. Small Steel Shield. Battered Scalemail.
        
        Background: This man, for whatever reason, has been hung multiple times. In each time he has survived, but around his neck are pretty severe scarring from those events. His survival has given him a sense of purpose, and almost a sense of indestructability. 
        
        \subsection{The Weasel} STR 14 (+1) DEX 18 (+3) CON 15 (+1) INT 9 (+0) WIS 11 (+0) CHA 6 (-2). Fighter. HP 11. Primary Attributes: STR, DEX, CON. Archetype: Fencer. Carrying Capacity: 22. 
        
        Inventory: Rapier. Buckler. Studded Leather Armour.   
        
        Background: This man has beady black eyes, stringly and tightly built muscles and a thin frame that is lithe and agile. It is immediately obvious that he is highly athletic, what is not obvious is that one day he wants to be a master of death.
