\paragraph{Experience}
Adventures are dangerous, but the rewards are great. All characters that make it through an adventure alive receive experience points (XP). Experience points are gained from two sources while on adventures: treasure and monsters. 

Characters gain XP from treasure they recover from the dungeon or wilderness and bring back to civilization. For purposes of earning XP, “civilization” is the nearest friendly town or stronghold. Sometimes figuring out how to get a dragon’s hoard back to town can be an adventure in itself. 

The characters receive 1XP per 1 gold piece (gp) value of coin, gems, jewellery, and special treasure (e.g., art, furs, silks) recovered on adventures. If the characters recover equipment on adventures, they must immediately sell the equipment for coin to get XP. If they keep the equipment for later use, they receive no XP from it. If the party recovers magic items on an adventure, and sells them without using them, they receive 1XP per 1gp earned in the sale. If the characters use the magic items, they do not get any XP, even if they later sell them. (This is to prevent characters from using magic items to help them adventure, then selling the magic items for XP later, essentially benefiting twice from the same item.) 

Characters do not earn treasure XP from wages earned or business transactions – this is not treasure recovered from an adventure. Characters also do not earn treasure XP from recovering monster parts on adventures – this is experience from monsters. 

\paragraph{EXPERIENCE FROM MONSTERS}

All defeated monsters (either outsmarted, captured, or killed), grant XP based on how powerful they are. Monsters begin with a base XP determined by Hit Dice (HD), and receive a bonus for each special ability they have (fire breath, spell-like abilities, etc.). Refer to the Monster Experience Points table below. To determine the number of special abilities a monster has, count the number of asterisks next to its Hit Dice in its Monster Listing in Chapter 8. 

To calculate a monster’s XP, begin with the base XP value for its Hit Dice. Add the value for the XP bonus per ability, multiplied by the number of special abilities the monster has. A lamia is a HD 9 with 3 special abilities, so her bonus XP is (3 x 600 = 1,800). A group of adventurers receives 2,500XP (700 + 1,800) for each lamia they defeat. 
\newline
\paragraph{Monster XP}
\begin{tabular}{l l l}
    Monster HD & Base XP & Bonus XP / Ability \\
    \hline
    Less than 1 & 5 & 1\\
    1 & 10 & 3\\
    1+ & 15 & 6 \\
    2 & 20 & 9\\
    2+ & 35 & 12 \\
    3 & 50 & 15 \\
    3+ & 65 & 35 \\
\end{tabular}
