\pagecolor{gray}\afterpage{\nopagecolor}
\fontfamily{pzc}
\selectfont
In the Midgaardian Keep, Castle Black, a young noble Lord aged 11 lays in bed. His servant, a short lady who has seen many years sits in a chair on the opposite side of the room. She knitts a scarf with delicate and refined movements. 

``Have I ever told you that my pappy fought in the Great War? It was a long time ago, your parents had'nt even been born yet.''

``I dont like those kind of stories. Knights in shining armour are not my thing.''

She chuckles, ``So what kind of stories do you like my little Lord.''

``The scary ones.''

``The Great War was scary my little Lord! It wasn't a romance tale like your sages say. 'The Days of Dread' - that's what we called life back then. There were no goodly kings then, no no. One House was composed of vile necromancers!''

``The Mordenheims? I read a bit of them, but my teachers constantly change the topic when I inquire further.''

``We didn't know them by their names then, young Lord, but we knew what they did. Long after the war had ended, Pappy would wake up in the night sometimes screaming. When I was grown I finally asked him why that happened, and he said: 'Every time I sleep I see my brother. But not... like you knew him, Helga. I see him when he was killed. And I see him when he rose again, and I see him when he tried to strangle me with his cold, dead hands. And finally, I see his walking corpse's head sliced clean off by my commander.' ''

The little Lord rests his head on his silk pillow. On his fair and normally jaded face curls a small smile. 

\normalfont