\paragraph{Pacing Structures}
\begin{tabular}{l l}
    Structure & Format \\
    \hline
    Vice & \\
    Pendulum & \\
    Pit & \\
    
\end{tabular}

\begin{description}
  \item[Shy/Frightened] tend to stay shruken and small. They hunch down and keep their arms close to their sides. Their eyes may dart about if especially nervous, and thy try to avoid physical or eye contact.
  \item[Bitter/Grizzled] frown and glare. Their lips are set in a permanent snarl. Their motions are lackadaisical (after all, what's the point?). They tend to sit back a lot, content to have things happen to them.
  \item[Authoritative] stand tall and proud. They make broad and sweeping motions to match their grand stature. All their gestures bespeak power and action. They might pound a fist into a palm or point at someone in condemnation.
  \item[Sinister] tend to look at the world through very wide eyes or narrow, squinty eyes. They often carry a wry smirk on their faces, as if they know something you dont.
  \item[Elderly] look bout with half-lidded eyes. They move slowly and gesture minimally. Their hands might shake while they are gesturing or speaking. Taken to an extreme, these mannerisms can also mark undead that bear the insufferable weight of countless centuries. Some move as still as possible; every movement had a specific purpose. Lichlike characters act as though indulging in any indication of life is a distasteful burden. 
  \item[Wise] look thoughtful. They may wear a slight frown upon their faces and listen before speaking, nodding sagely at every word. They may clasp a steady hand on someone's shoulder when about to give out a piece of advice. 
  \item[Spunky] cant help the grins on their faces. They like to wink at others or bite their lips in a sprightly way. They enjoy teasing and poking fun at others. They're always moving about in every direction.
  \item[Brooding/Angry] speak little. They glare steadfastly at those they address. They clench their jaw, ball their hands into fists and fold their arms.
  \item[Sad] often stare into space, pondering their woe. They move slowly, using little effort. They shuffle their feet and slump their shoulders. They may smile slightly, but their smile doesn't quite reach their eyes, and it falters quickly.
  \item[Calculating] stare at people for a long time, in order to assess them. They often look people up and down, scrutinizing them from head to foot. They think before they speak and move with very orderly, restrained gestures.
  \item[Manic] are never quite in control of their bodies. Whether madnen or under the influence they may continually twiddle their fingers. Their bodies are seldom still.
  \item[Happy/welcoming] often hold out their arms to people. They laugh often, even if it's just to humour their guests. They often touch or clasp their friends, giving them pats on the back or rubs of the shoulder.
  \item[Smug]
\end{description}

\paragraph{Investigate}
\begin{tabular}{l l}
    Library research & 1d4 Hours\\
    Stack of letters in a desk & 1d4 x 10 minutes\\
\end{tabular}
